%------------------------
% Arnab's Resume
% Author : Arnab Roy
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section format
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands

\newcommand{\resumeItem}[2]{
  \item\small{\textbf{#1}{: #2}}
}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4}
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\LARGE Arnab Roy} & \href{mailto:mr.roy.arnab@gmail.com}{mr.roy.arnab@gmail.com}\\
Phone: +91 9394255756 & 
\href{https://www.linkedin.com/in/arnabroy25/}{\underline{LinkedIn}} \quad
\href{http://github.com/arnabdotpy/}{\underline{GitHub}}
\end{tabular*}

%-----------EXPERIENCE-----------------

\section{Experience}

\resumeSubHeadingListStart

\resumeSubheading
{Physics Wallah}{Noida, India}
{Associate Software Engineer, Innovation}{2023 -- Present}

\resumeItemListStart

\resumeItem{Clicker App}
{Engineered an interactive classroom response system integrating ESP8266 hardware with Android devices to enable real-time student participation; contributed to securing deployment with the Andhra Pradesh Government.}

\resumeItem{PiBook Appstore}
{Contributed to the development of the App Store for PiBook, a low-cost Android laptop developed at PW Innovations to make laptops affordable for students.}

\resumeItem{PW Drona App}
{Built and scaled the PW Drona App (Android \& iOS) to improve teacher productivity; the application is live on the Play Store and App Store.}

\resumeItem{GATE Rank Predictor}
{Built a rank prediction system that programmatically scraped student response sheets, parsed and evaluated answers against official answer keys, and applied scoring algorithms to compute estimated ranks.}

\resumeItem{Engineering \& DevOps}
{Built and maintained multiple production-grade web and mobile applications while managing DevOps infrastructure, designing CI/CD pipelines, and mentoring developers across the engineering team..}

\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------

\section{Projects}

\resumeSubHeadingListStart

\resumeSubItem{Younity}
{Developed a smart classroom platform for YouTube live classes enabling students to poll, ask doubts, and interact during lectures while teachers monitor real-time insights through an Electron-based dashboard displayed on MaxHub boards.}

\resumeSubItem{VNC Android Remote}
{Built a mobile-based virtual remote application allowing users to control TVs via smartphones using the VNC protocol for real-time screen interaction and command transmission.}

\resumeSubItem{Pixel Art Display}
{Engineered an ESP32-powered 16x16 LED pixel display with BLE communication, developing embedded firmware and a mobile pipeline to stream 2D pixel art to the device in real time.}

\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------------

\section{Achievements}

\begin{itemize}
\item Star Performer of the Month (July 2023), Physics Wallah for exceptional engineering contributions and dedication in product development.
\item Runner Up - Hacked By PW (Internal Hackathon at Physics Wallah) Won an international trip to Thailand.
\end{itemize}

%-----------LEADERSHIP-----------------

\section{Leadership \& Activities}

\resumeSubHeadingListStart

\resumeSubItem{Minister of Digital Infrastructure – Student Cabinet, Bennett University}
{Leading technology initiatives and managing digital infrastructure for the Student Cabinet. (Aug 2025 -- Present)}

\vspace{2pt}

\resumeSubItem{Chief Technology Officer – Computer Society of India, Bennett University}
{Led the technical team and infrastructure for the CSI student chapter and supported development of technical platforms and events. (Aug 2024 -- May 2025)}

\vspace{2pt}

\resumeSubItem{Lead Organizer – Hackaccino Hackathon, Bennett University}
{Co-led a 5-member team to organize a university hackathon and built an automated registration and event tracking platform to streamline participant management. (2024 -- 2025)}

\vspace{2pt}

\resumeSubItem{Community Manager – Creator Communities}
{Built and managed creator communities including GetSetFly Science (9.7M+ subscribers) and Tharun Speaks (900K+ subscribers). (2023)}

\resumeSubHeadingListEnd

%-----------EDUCATION-----------------

\section{Education}

\resumeSubHeadingListStart

\resumeSubheading
{Bennett University}{India}
{B.Tech in Computer Science Engineering | CGPA: 8.30/10}{2023 -- Present}

\resumeSubheading
{Maharishi Vidya Mandir}{India}
{Class XII | 85.4\%}{2023}

\resumeSubheading
{Rowlands Memorial High School}{India}
{Class X | 85.5\%}{2021}

\resumeSubHeadingListEnd

%-----------SKILLS-----------------

\section{Technical Skills}

\resumeSubHeadingListStart

\resumeSubItem{Languages}{JavaScript, TypeScript, Python, C++, Java, HTML, CSS}

\resumeSubItem{Frameworks \& Libraries}{React, React Native, Express, NestJS, Flask, FastAPI, TailwindCSS, Zustand, Socket.IO, Mongoose, Electron}

\resumeSubItem{Databases}{MongoDB, PostgreSQL, MySQL, SQLite, Redis}

\resumeSubItem{Embedded \& IoT}{ESP8266, ESP32, Arduino IDE, PlatformIO, BLE (Bluetooth Low Energy), MQTT}

\resumeSubItem{DevOps \& Infrastructure}{Linux, Git, GitHub, GitLab, Docker, Nginx, Reverse Proxies, SSL (Let's Encrypt), CI/CD Pipelines, Coolify, Cloudflare, Google Cloud Platform}

\resumeSubItem{Platforms \& Tools}{Firebase, Supabase, Appwrite, Play Store Deployment, App Store Deployment, Figma}

\resumeSubHeadingListEnd

\end{document}